Preliminary Draft

### 2021-07-20 article/draft.tex
few changes

\usepackage{titlesec}

@@

@@

A number of recent studies  point towards the idea that ``Fake News'' or disinformation is a small subset of the total supply of information on online social networking platforms (e.g. Grinberg et al. (2019)~\cite{grinberg} and Broniatowski et al. (2020)~\cite{broniatowski}). Yet, this seemingly small subset is generating great concern in traditional media and in society in a broader sense. \footnote{For example see the February 2020 \href{https://www.who.int/director-general/speeches/detail/munich-security-conference}{speech} of the Director General of the WHO at the Munich Security Conference, where he says ``But we’re not just fighting an epidemic; we’re fighting an infodemic.'' Furthermore, the European commission recognizes the spread of online disinformation as a problem and has put together in 2018 a \href{https://digital-strategy.ec.europa.eu/en/policies/code-practice-disinformation}{Code of practice on Disinformation}, which is a set of self-regulatory standards to fight disinformation. {\color{pink} Add more examples to show that this problem is highlighted by different institutions with different/neutral political color.. }}

Section $230$ in the United States Communications Decency Act provides immunity for website platforms against the content created by users. Similar regulations exist in the European Union via the E-commerce Directive (2000) in articles $12$ and $15$.\footnote{See section $4$ in Bayer (2019)~\cite{Bayer} for a comprehensive overview of the mentioned articles.} Nevertheless, there is growing pressure for Mainstream Social Media Platforms (hereafter MSMP), such as Facebook, Twitter or Youtube, to moderate the available content. In particular, platforms take explicit actions when content is in violation of local laws in different jurisdictions, e.g. laws regarding defamation of a racial nature, dissemination of symbols from unconstitutional organizations, privacy protection, digital security, electoral laws. Facebook reports having implemented a total of $64.7$ thousand content restrictions based on local law across all countries in 2020.\footnote{See Facebook Transparency Center, Content restrictions based on Local Law: \href{https://transparency.fb.com/data/content\-restrictions}{transparency.fb.com/data/content\-restrictions}. We summed the count of content restrictions over all countries reported in the table, for $H1$ and $H2$ of the year 2020.} Google reports a total of $26$ thousand government requests to remove content from July 2020 to December 2020, among which $11.4$ thousand concerned Youtube.\footnote{See Google's Transparency report, government requests to remove content: \href{https://transparencyreport.google.com/government-removals/overview}{transparencyreport.google.com/government-removals/overview}.} Twitter reports having received $42.2$ thousand legal demands from third-parties from January to June 2020, and has responded by withholding $82$ thousand accounts and $3.1$ thousand tweets.\footnote{See Twitter Transparency website, Removal requests: \href{https://transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}{transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}.}

@@

Furthermore, MSMP are increasingly engaging in editorial tasks by implementing targeted policies to insure that each platform's rules are not violated. Community guidelines of Facebook, Twitter and Youtube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include sub-categories such as violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam.\footnote{For an exhaustive overview of the community standards of Facebook, see: \href{https://www.facebook.com/communitystandards/}{facebook.com/communitystandards/}. For the Twitter  Rules see: \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{help.twitter.com/en/rules-and-policies/twitter-rules}, and for Youtube community guidelines see: \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/policies/community\-guidelines/}{youtube.com/intl/en\_us/howyoutubeworks/policies/community\-guidelines/}.} While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries.

@@

During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content.\footnote{For Facebook, Twitter and Youtube see respectively the following updates concerning COVID19 related misinformation policies: \href{https://support.google.com/youtube/answer/9891785}{https://support.google.com/youtube/answer/9891785}, \href{https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy}{help.twitter.com/en/rules-and-policies/medical-misinformation-policy} and \href{https://support.google.com/youtube/answer/9891785}{support.google.com/youtube/answer/9891785}.} Those policies are enforced via existing actions used by the platforms to tackle other rules' violations, such as: labelling content to provide more context or indicate falsehood, publishing a list of terms or topics that will be flagged\footnote{{\color{pink} put here the list of Facebook and Twitter terms about covid.}}, suspending accounts, implementing strike systems, reducing the visibility of content, etc. As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms. Such targeted policies show the willingness of MSMP to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general. In particular, policies regarding misinformation are not part of the set of platform rules or community guidelines\footnote{As of July 2021.}. The 2019 report of the Facebook Data Transparency Advisory Group\footnote{To read the full report, see: \href{https://law.yale.edu/yls-today/news/facebook-data-transparency-advisory-group-releases-final-report?fbclid=IwAR2xMZr5GdD1GaNpjsXR3\_yeeIR4H9iFASfrni5HKcJVAO5oWA52bvwcZxU}{https://law.yale.edu/yls-today/news/facebook-data-transparency-advisory-group-releases-final-report?fbclid=IwAR2xMZr5GdD1GaNpjsXR3\_yeeIR4H9iFASfrni5HKcJVAO5oWA52bvwcZxU}.} (DTAG) states that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report.}''. Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform. It is explained via a blog post on the facebook Newsroom.\footnote{See: \href{https://about.fb.com/news/2018/05/hard-questions-false-news/}{https://about.fb.com/news/2018/05/hard-questions-false-news/}.}. Similarly, Twitter communicates about actions related to misinformation via their Twitter Safety Blog/account\footnote{See \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{https://blog.twitter.com/en\_us/authors.TwitterSafety}.}. In a post on Youtube Official Blog\footnote{See \href{https://blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}{https://blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}.}, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation.

@@

In this article, we focus on MSMP's policies and actions regarding content with low credibility or false information, commonly referred to as {\it Fake News}.\footnote{For an overview on the {\it concept} of {\it Fake News}, we refer the reader to the article The science of fake news by Lazer et al. (2018)~\cite{lazer}.} The {\it Fake News} phenomenon is still ill-defined by the academic community, as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience. In particular, the intricacies of constructing a legal framework concerning misinformation and disinformation arises from the difficulty of identifying and qualifying a piece of online content as false or misleading, among an overwhelming quantity of daily produced content, without infringing existing laws.\footnote{See \href{https://www.poynter.org/ifcn/anti-misinformation-actions/}{A guide to anti-misinformation actions around the world} on the website of Poynter Institute.} The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation. Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources. In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral. This gave rise to a set of heterogenous fact-checking policies across mainstream platforms. For example, Facebook has a substantial partnership program with Fact-checking partners certified by the non-partisan International Fact-Checking Network.\footnote{For an overview of Facebook's third-party fact checking program see: \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}.} Facebook use a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section} Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy. The Twitter Safety Team tweeted on June 3, 2020 the following:  ``We heard: 1. Twitter shouldn’t determine the truthfulness of Tweets 2. Twitter should provide context to help people make up their own minds in cases where the substance of a Tweet is disputed. Hence, our focus is on providing context, not fact-checking.'' Tweet ID \href{https://twitter.com/TwitterSafety/status/1267986503721988096}{1267986503721988096}.} and the platform is testing a new system based on the wisdom of the crowds to tackle misinformation (see \href{https://blog.twitter.com/en\_us/topics/product/2021/introducing-birdwatch-a-community-based-approach-to-misinformation}{Twitter Birdwatch}). As for Youtube, this platform utilizes the \href{https://schema.org/ClaimReview}{schema.org ClaimReview} markup, where fact-checking articles created by eligible publishers can appear on information panels. \footnote{See \href{https://support.google.com/youtube/answer/9229632}{https://support.google.com/youtube/answer/9229632}.}

@@

Nevertheless, misinformation specific interventions by MSMP are hard to monitor, study or verify by third parties (e.g. academic community, data journalists, NGOs), as in many cases misleading or false content does not qualify as a violation of a given platform's rules and it does not explicitly appear as a separate category in available transparency reports. This makes the study of online misinformation, the assessment of the impact of platforms' actions to tackle misinformation and their relevancy a burdensome task for the academic community. Hence, in the present article we explain how to verify with data mining MSMP's current actions regarding content with low credibility or false information. We do so by providing a series of examples for different interventions and platforms. For the purpose of clarity, we only focus on three platforms: Facebook, Twitter and Youtube. Both Facebook and Youtube are in the top three most popular social media platforms in terms of number of users.\footnote{See for example the ranking of the most popular social networks as of April 2021 on Statista: \href{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}.} We further choose Twitter because it is a social networking platform with the most news-focused users, according to the Pew Research center (2019)~\cite{pew1}. More specifically, we survey a number of common policies used in order to tackle misinformation, across the three above cited MSMP, Facebook, Twitter and Youtube: temporary or permanent suspension of users, reducing the visibility of some content, introducing flags and notices. We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies.\footnote{For a detailed list of interventions check the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}. } We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring. We summarize in table \ref{tab1} the tools used to collect the data from Facebook, Twitter and Youtube, that we use in multiple examples throughout the present article. We compile in Appendix \ref{links} in table \ref{summary}, URL links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and Youtube. Finally, we discuss how an increased effort of transparency regarding specific content can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.  %the announced policy for a specific user was implemented or not.

@@

\section{Policies}

\subsection{Temporary suspension and Permanent suspension}

@@

\begin{figure}
	\centering
		%\begin{multicols}{1}
			\includegraphics[scale=0.3]{./img/fb/fig1_fb.png}
		%\end{multicols}
	\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J. Trump} between January $1$, $2020$ and June $15$, $2021$. The data corresponds to $6$ $083$ posts retrieved from the CrowdTangle API using the {\it posts} endpoint.}
	\label{fig1_fb}
\end{figure}

@@

@@

\subsubsection{Twitter}

\begin{figure}
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/lifesite.jpg} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/lifesite_rolling_7_lifesite.jpg}
	%\end{multicols}
\caption{Panel (a): number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Panel (b): number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

@@

@@

\subsubsection{Youtube}

@@

\begin{figure}
	\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.24]{./img/oann/fig1_oann.png}
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.25]{./img/oann/fig2_oann.png} 
	%\end{multicols}
	\caption{panel (a): Number of Youtube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021. Panel (b): accumulated view counts for videos. The metrics correspond to the videos’  publishing date and the data is retrieved from the youtube API with the {\it playlists} and  {\it videos} endpoints. }
	\label{fig1_oann}
\end{figure}

>>>>

\usepackage{titlesec}
\usepackage[font=footnotesize,labelfont=bf]{caption}

@@

\tableofcontents

@@

Section $230$ in the United States Communications Decency Act provides immunity for website platforms against the content created by users. Similar regulations exist in the European Union via the E-commerce Directive (2000) in articles $12$ and $15$.\footnote{See section $4$ in Bayer (2019)~\cite{Bayer} for a comprehensive overview of the mentioned articles.} Nevertheless, there is growing pressure for Mainstream Social Media Platforms, such as Facebook, Twitter or Youtube, to moderate the available content. In particular, platforms take explicit actions when content is in violation of local laws in different jurisdictions, such as laws regarding defamation of a racial nature, dissemination of symbols from unconstitutional organizations, privacy protection, digital security, electoral laws. For example, Facebook reports having implemented a total of $64.7$ thousand content restrictions based on local law across all countries in 2020.\footnote{See Facebook Transparency Center, Content restrictions based on Local Law: \href{https://transparency.fb.com/data/content\-restrictions}{transparency.fb.com/data/content\-restrictions}. We summed the count of content restrictions over all countries reported in the table, for $H1$ and $H2$ of the year 2020.} %Google reports a total of $26$ thousand government requests to remove content from July 2020 to December 2020, among which $11.4$ thousand concerned Youtube.\footnote{See Google's Transparency report, government requests to remove content: \href{https://transparencyreport.google.com/government-removals/overview}{transparencyreport.google.com/government-removals/overview}.} Twitter reports having received $42.2$ thousand legal demands from third-parties from January to June 2020, and has responded by withholding $82$ thousand accounts and $3.1$ thousand tweets.\footnote{See Twitter Transparency website, Removal requests: \href{https://transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}{transparency.twitter.com/en/reports/removal-requests.html\#2020-jan-jun}.}

@@

Furthermore, mainstream platforms are increasingly engaging in editorial tasks by implementing targeted policies to insure that each platform's rules are not violated. Community guidelines of Facebook, Twitter and Youtube can be summarized in a handful of categories, regarding safety, privacy and authenticity; which include sub-categories such as violence, terrorism, child sexual exploitation, abuse, harassment, hateful conduct, suicide or self-harm, illegal or regulated goods and services, platform manipulation and spam (see table \ref{summary} in Appendix \ref{links}). While specific to each platform, the previously cited categories correspond in most cases to well defined concepts that fall into legal frameworks in many countries, unlike misinformation. The intricacies of constructing a legal framework for misinformation arises from the difficulty of identifying and qualifying a piece of online content as false or misleading, among an overwhelming quantity of daily produced content, without infringing existing laws.\footnote{See \href{https://www.poynter.org/ifcn/anti-misinformation-actions/}{A guide to anti-misinformation actions around the world} on the website of Poynter Institute.} In particular, a number of recent studies  point towards the idea that ``Fake News'' or disinformation is a small subset of the total supply of information on online social networking platforms (e.g. Grinberg et al. (2019)~\cite{grinberg} and Broniatowski et al. (2020)~\cite{broniatowski}). Yet, this seemingly small subset is generating great concern in traditional media and in society in a broader sense. \footnote{For example see the February 2020 \href{https://www.who.int/director-general/speeches/detail/munich-security-conference}{speech} of the Director General of the WHO at the Munich Security Conference, where he says ``But we’re not just fighting an epidemic; we’re fighting an infodemic.'' Furthermore, the European commission recognizes the spread of online disinformation as a problem and has put together in 2018 a \href{https://digital-strategy.ec.europa.eu/en/policies/code-practice-disinformation}{Code of practice on Disinformation}, which is a set of self-regulatory standards to fight disinformation. {\color{pink} Add more examples to show that this problem is highlighted by different institutions with different/neutral political color.. }}

@@

In this article, we focus on mainstream platforms' policies and actions regarding content with low credibility or false information, commonly referred to as {\it Fake News} (for an overview of the concept see Lazer et al. (2018)~\cite{lazer}). The {\it Fake News} phenomenon is still ill-defined by the academic community, as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience.  The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation. Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources. In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral. This gave rise to a set of heterogenous fact-checking policies across mainstream platforms. For example, Facebook has a substantial partnership program with Fact-checking partners certified by the non-partisan International Fact-Checking Network. Facebook use a number of signals and machine learning models to predict misinformation and surface it to fact-checkers.\footnote{See the \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{section} Frequently asked questions: `How does Facebook use technology to detect potential misinformation?''} Twitter seems to have a different approach where they focus on providing context rather than fact-checking\footnote{To the best of our knowledge, Twitter does not have a page which summarizes its fact-checking strategy. The Twitter Safety Team tweeted on June 3, 2020 the following:  ``We heard: 1. Twitter shouldn’t determine the truthfulness of Tweets 2. Twitter should provide context to help people make up their own minds in cases where the substance of a Tweet is disputed. Hence, our focus is on providing context, not fact-checking.'' Tweet ID \href{https://twitter.com/TwitterSafety/status/1267986503721988096}{1267986503721988096}.} and the platform is testing a new system based on the wisdom of the crowds to tackle misinformation (see \href{https://blog.twitter.com/en\_us/topics/product/2021/introducing-birdwatch-a-community-based-approach-to-misinformation}{Twitter Birdwatch}). As for Youtube, this platform utilizes the \href{https://schema.org/ClaimReview}{schema.org ClaimReview} markup, where fact-checking articles created by eligible publishers can appear on information panels (see table \ref{summary} in Appendix \ref{links}).

@@

During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content (see table \ref{summary} in Appendix \ref{links}). Those policies are enforced via existing actions used by the platforms to tackle other rules' violations, such as: labelling content to provide more context or indicate falsehood, publishing a list of terms or topics that will be flagged\footnote{{\color{pink} put here the list of Facebook and Twitter terms about covid.}}, suspending accounts, implementing strike systems, reducing the visibility of content, etc. As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms. Such targeted policies show the willingness of mainstream platforms to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general. In particular, policies regarding misinformation are not part of the set of platform rules or community guidelines\footnote{As of July 2021.}. The 2019 report of the Facebook Data Transparency Advisory Group\footnote{To read the full report, see: \href{https://law.yale.edu/yls-today/news/facebook-data-transparency-advisory-group-releases-final-report?fbclid=IwAR2xMZr5GdD1GaNpjsXR3\_yeeIR4H9iFASfrni5HKcJVAO5oWA52bvwcZxU}{https://law.yale.edu/yls-today/news/facebook-data-transparency-advisory-group-releases-final-report?fbclid=IwAR2xMZr5GdD1GaNpjsXR3\_yeeIR4H9iFASfrni5HKcJVAO5oWA52bvwcZxU}.} (DTAG) states that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report.}''. Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform. It is explained via a blog post on the facebook Newsroom.\footnote{See: \href{https://about.fb.com/news/2018/05/hard-questions-false-news/}{https://about.fb.com/news/2018/05/hard-questions-false-news/}.}. Similarly, Twitter communicates about actions related to misinformation via their Twitter Safety Blog/account\footnote{See \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{https://blog.twitter.com/en\_us/authors.TwitterSafety}.}. In a post on Youtube Official Blog\footnote{See \href{https://blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}{https://blog.youtube/inside-youtube/the-four-rs-of-responsibility-raise-and-reduce/}.}, the platform explained its ``Four Rs of Responsibility" and how it raises authoritative content, reduces borderline content and harmful misinformation.

@@

Nevertheless, misinformation specific interventions by mainstream platforms are hard to monitor, study or verify by third parties (e.g. academic community, data journalists, NGOs), as in many cases misleading or false content does not qualify as a violation of a given platform's rules and it does not explicitly appear as a separate category in available transparency reports. This makes the study of online misinformation, the assessment of the impact of platforms' actions to tackle misinformation and their relevancy a burdensome task for the academic community. Hence, in the present article we explain how to verify with data mining mainstream platforms' current actions regarding content with low credibility or false information. We do so by providing a series of examples for different interventions and platforms. We only focus on three platforms: Facebook, Twitter and Youtube. Both Facebook and Youtube are in the top three most popular social media platforms in terms of number of users.\footnote{See for example the ranking of the most popular social networks as of April 2021 on Statista: \href{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}.} We further choose Twitter because it is a social networking platform with the most news-focused users, according to the Pew Research center (2019)~\cite{pew1}. More specifically, we survey a number of common policies used in order to tackle misinformation, across the three above cited mainstream platforms, Facebook, Twitter and Youtube: temporary or permanent suspension of users, reducing the visibility of some content, introducing flags and notices. We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies.\footnote{For a detailed list of interventions check the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}. } We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring. We summarize in table \ref{tab1} the tools used to collect the data from Facebook, Twitter and Youtube, that we use in multiple examples throughout the present article. We compile in Appendix \ref{links} in table \ref{summary}, URL links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and Youtube. Finally, we discuss how an increased effort of transparency regarding specific content can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.  %the announced policy for a specific user was implemented or not.

@@

\section{Temporary \& permanent suspension}

@@

\subsection{Facebook}

@@

\begin{figure}[h]
	\centering
		%\begin{multicols}{1}
			\includegraphics[scale=0.3]{./img/fb/fig1_fb.png}
		%\end{multicols}
	\caption{Number of Facebook posts published each day by the Facebook page {\it Donald J. Trump} between January $1$, $2020$ and June $15$, $2021$. The data corresponds to $6$ $083$ posts retrieved from the CrowdTangle API using the {\it posts} endpoint.}
	\label{fig1_fb}
\end{figure}

@@

\subsection{Twitter}

@@

\begin{figure}[h]
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/lifesite.jpg} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/lifesite_rolling_7_lifesite.jpg}
	%\end{multicols}
\caption{Panel (a): number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Panel (b): number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

\subsection{Youtube}

\begin{figure}[h]
	\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.21]{./img/oann/fig3_oann.png}
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.31]{./img/tony/fig3_tony.png}
	%\end{multicols}

%\smallskip

\begin{figure}[h]
	\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.27]{./img/oann/fig1_oann.png}
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.26]{./img/oann/fig2_oann.png} 
	%\end{multicols}
	\caption{panel (a): Number of Youtube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021. Panel (b): accumulated view counts for videos. The metrics correspond to the videos’  publishing date and the data is retrieved from the youtube API with the {\it playlists} and  {\it videos} endpoints. }
	\label{fig1_oann}
\end{figure}

%\smallskip
\begin{figure}[h]
	\centering
		%\begin{multicols}{1}
			\includegraphics[scale=0.35]{./img/tony/fig1_tony.png}
		%\end{multicols}
		%\begin{multicols}{1}
			\includegraphics[scale=0.34]{./img/tony/fig2_tony.png}
		%\end{multicols}
	\caption{Panel (a): Number of Youtube videos uploaded each day by the Youtube channel {\it Tony Heller} between September 1, 2020 and November 15, 2020. Panel (b): accumulated view counts for videos uploaded by the same Youtube channel. The date corresponds to the videos’  publishing date. 
}
	\label{fig1_tony}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Flags, Notices and labels}

\subsection{Facebook}

To the best of our knowledge, two types of flags can currently be seen on Facebook posts, videos and pictures: $(i)$ information banners that do not refute the message in the post but that give a link to an authoritative source, such as ``Visit the COVID-19 Information Centre for vaccine resources'' and $(ii)$ fact-check flags that provide a ``judgement'' on the text of the post or the link, shared, such as ``False information Checked by independent fact-checkers'' (see Figure \ref{fb_flags}). The fact-check flags can be of varied nature : `False', `Partly false', `Missing context', `False headline', `Altered media', `Opinion', `Satire', `Not eligible' and even `True'.

\begin{figure}[h]
\centering
\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_1.png}
\includegraphics[scale=0.35]{./img/fb_flags/fb_flag_2.png}
\includegraphics[scale=0.49]{./img/fb_flags/fb_flag_3.png}
\caption{Examples of Facebook posts having shared a link fact-checked as False by one of Facebook’s partners. Screenshots taken on July 8, 2021: \href{https://www.facebook.com/groups/1220117708132394/permalink/2386760061468147}{facebook.com/groups/1220117708132394/permalink/2386760061468147},  \href{https://www.facebook.com/groups/473809623000471/permalink/1333200093728082}{facebook.com/groups/473809623000471/permalink/1333200093728082}, \href{https://www.facebook.com/691911990845585/posts/3835629366473816}{facebook.com/691911990845585/posts/3835629366473816}).} 
\label{fb_flags}
\end{figure}

We first searched for all the Facebook posts having shared a link rated as ‘False’ by Science Feedback with the {\it search} endpoint in minet\footnote{ link: \href{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html}{https://beforeitsnews.com/eu/2021/04/stay-away-from-the-vaxxed-it-is-official-from-pfizers-own-documents-2671454.html} and its fact-check: \href{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}{https://healthfeedback.org/claimreview/insufficient-evidence-to-claim-covid-19-vaccines-cause-menstrual-irregularities-in-vaccinated-women-vaccinated-people-arent-making-unvaccinated-people-ill/}).}. Twenty Facebook posts were collected this way, and the newly developed scraper was used to verify whether they were flagged with an information banner, a fact-check flag, both or none. Three posts were unavailable, and thus could not be categorized by the scraper. As Science Feedback has sent a False fact-check for this link to Facebook, we would expect all these posts to contain a fact-check flag, but we had no expectations for the information banner.

@@

Surprisingly only $11$ posts out of the remaining $17$ had a ‘False information’ flag  (Table \ref{tab_flags_fb}, see left panel of Figure \ref{fb_flags} for an example). We observed that the flagged posts were also the ones in which the false link was expanded (i.e., a banner was visible with an image of the link and that can be clicked on, see the middle and right panels of Figure \ref{fb_flags} for examples). As the ‘False information’ flag is applied on the link banner, and not on the link itself, a user is thus able to share a False link on Facebook without the ‘False information’ banner if the link is not expanded.

\begin{table}[h]
\begin{tabular}{|c|c|c|c|}
\hline
\multicolumn{4}{|c|}{Number of posts}                                                                                                                    \\ \hline
with no flag & with an information flag & with a fact-check flag & \begin{tabular}[c]{@{}c@{}}with a fact-check and an \\  information flags\end{tabular} \\ \hline
0            & 7                        & 4                      & 7                                                                                     \\ \hline
\end{tabular}
\caption{Count for the Facebook posts with the different types of flags having shared a link fact-checked False by one of Facebook’s partners}
\label{tab_flags_fb}
\end{table}

We also observed that most of the posts sharing this False link (13 out of 17, Table \ref{tab_flags_fb}) had an information banner saying ‘Visit the COVID-19 Information Centre for vaccine resources’ (see the first two examples of Figure \ref{fb_flags}). We could not identify why the banner was applied on some posts and not on others (we saw no clear difference in the post messages for example). It should be noted that some posts displayed both the information and the fact-check banners, as in the middle panel of Figure \ref{fb_flags}.

\subsection{Twitter}

Alongside other social networking platforms, when the content of a tweet violates the Twitter rules, a notice can be added to provide more context according to Twitter's Help Center.\footnote{See Notices on Twitter and what they mean: \href{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}.} At the tweet level, notices take the form of a label or an interstitial. Labels are context specific (e.g. COVID19 or presidential elections) and  redirect users to a URL to get more context, for example ``Get the facts about COVID-19'' (see right panel of figure \ref{fig8}). Interstitials are presented as a greyed box on top of a tweet, which indicate sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts, for example ``The following media includes potentially sensitive content'' (see left panel of figure \ref{fig_notice}). At the account level, notices can also indicate whether an account has been temporarily or permanently suspended.

%\smallskip

\begin{figure}[h]
\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-06-30_2.png}
   	 %\end{multicols}
	%\begin{multicols}{1} 
		\includegraphics[scale=0.32]{./img/tweets/Capture_2021-06-30.png}
	%\end{multicols}
	\caption{Two tweets sharing the same URL link marked as False by a Fact-Checker, screenshots taken on June 20, 2021. Panel (a): Tweet ID \href{https://twitter.com/davidjcaron/status/1241088065462026242}{1241088065462026242} without a label. Panel (b): Tweet ID \href{https://twitter.com/reactiveIntent/status/1261876171584745472}{1261876171584745472} containing a label.}
	\label{fig8}
\end{figure}

To the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a tweet is labeled or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the API. Hence, in order to investigate the presence of labels of all types, we resorted to scrape Twitter data using Minet [5]. This tool was recently enriched upon our request in order to capture whether a tweet contains a label or not, via the {\it minet twitter scrape} command.

@@

In this section, we take a deeper look at how labels and notices are introduced by Twitter, to indicate content which is inaccurate or false. To that end, we gathered a set of $3094$ URL links of articles which were marked as $False$ by Science Feedback, a fact-checking organization verifying the credibility of science-related viral information. As a second step, we collected (on June 30, 2021) via Minet Command line tool~\cite{minet} all the tweets that have shared a URL link which belongs to the set of $3094$ links marked as $False$. This data collection resulted in $323$ $938$ tweets, excluding retweets. Only $28$ tweets contained the label { ``Get the facts about COVID-19''}, $5$ tweets contained the label { ``Learn about US 2020 election security efforts''} and only $1$ had the following label {``This claim about election fraud is disputed''}. Furthermore, we noticed that the labeling rule might not be applied uniformly on a given set of tweets sharing the exact same URL link, among the set of collected tweets. More specifically, exactly $657$ tweets had shared a URL link redirecting to a video on Bitchute, entitled ``Important information on coronavirus 5G Kung Flu''. Among those $657$ tweets only $3$ contained the label ``Get the facts about COVID-19'' (see figure \ref{fig8}). This points towards the non-automation of the tweet labelling process and that it might be that these $3$ tweets were the only ones reported by a user.

\begin{figure}[h]
	\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01_2.png} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01.png}
	%\end{multicols}
	\caption{Panel (a): Tweet containing a URL link hidden behind an interstitial. Panel (b): when clicking on $view$, to view the content hidden behind the interstitial. Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}. Screenshots taken on July 1, 2021. }
	\label{fig_notice}
\end{figure}
